Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

### Research Question

To what extent do teaching methods supporting self-confidence impact the rate of entrepreneurship across OECD countries?

### Literature Review

### Estimation Strategy

#### Causal Chain

Education system / Teaching reinforcing self-esteem ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
<br>

>>>>

Henceforth, we expect to find out to what extent the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries.

We expect to observe the following causal chain :

Education system / Teaching reinforcing self-esteem ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
